### 2024-12-02 README.Rmd
remove local file reference

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(embeddings.model.path = "~/Documents/data/embeddings")
```

@@

glove_twitter_25d <- load_embeddings("glove.twitter.27B.25d")
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

glove_twitter_25d <- load_embeddings("glove.twitter.27B.25d", save = FALSE)
```
